Flat-histogram method comparison on the 2D Ising model

### 2020-05-08 ising/ising-body.tex
made some changes in conclusion.

\section{Conclusion}
We find that both SAD, 1/t-WL, and WL followed by a production run
(with an adequately small $\gamma^{\min}$) demonstrate excellent and robust
convergence. They all converge more rapidly than SAMC, and unlike pure WL do
not suffer from
error saturation. We find that for larger systems SAD reduces the updated factor
more slowly (and conservatively) than 1/t-WL and WL followed by a
production run. This means that SAD will take
proportionately more moves to converge to the same value as 1/t-WL as system
size is increased. SAD requires the user to specify a temperature range of
interest rather than an energy range of interest as the WL methods do. The 2D
Ising model is a system where the energy range is known \emph{a priori.}, which
makes a comparison between WL methods and SAD (which requires a minimum
temperature) more biased towards WL methods. For the majority of cases in which
the energy range of the system is not known and where a range of desired
temperatures is known, this will make the SAD method
considerably more convenient. This work also visually demonstrates
that WL followed by a production run performs extremely well and is preferable
to pure WL for ensuring both ergodicity and detailed balance.

\section{Acknowledgments}

We wish to thank Johannes Zierenberg for helpful discussions regarding WL followed by a production run and for insights into properties of a production run at different stages of convergence.

>>>>

\section{Conclusion}
We find that SAD, 1/t-WL, and WL followed by a production run
(with an adequately small $\gamma^{\min}$) demonstrate excellent and robust
convergence. They all converge more rapidly than SAMC, and unlike pure WL do
not suffer from
error saturation. We find that for larger Ising systems SAD reduces the update
factor more slowly (and conservatively) than 1/t-WL and WL followed by a
production run. This means that SAD will take
proportionately more moves to converge to the same value as 1/t-WL as system
size is increased (WL methods are given the energy range \emph{a priori.} and
converge independent of system size). SAD requires the user to specify a
temperature range of interest rather than an energy range of interest as the WL
methods do. The 2D
Ising model is a system where the energy range is known \emph{a priori.}, which
makes a comparison between WL methods and SAD (which requires a minimum
temperature) more biased towards WL methods. For the majority of cases in which
the energy range of the system is not known and where a range of desired
temperatures is known, this will make the SAD method
considerably more convenient. This work also visually demonstrates
that WL followed by a production run performs extremely well and is preferable
to pure WL for ensuring both ergodicity and detailed balance.

\section{Acknowledgments}
We wish to thank Johannes Zierenberg for helpful discussions regarding WL followed by a production run and for insights into properties of a production run at different stages of convergence.
